### 2023-04-21 Documentation/UFMG/PFCII/Metodology/Metodology.tex
documentation

This chapter is about describing the metodology and developments to achieve the project goals. 
The python routine which this project is about was developed by the previous student that worked on it.\cite{Monica}
The works therefore presented here are a continuation and optimization of the routine to make it more precise and applicable to both industrial and research approaches.

@@

    \subsection{Data Acquisition Thread}

@@

    The software was previously developed as a electrospray multipurpose library\cite{Monica}. 
    Continuing this methodology, in the setup json file there is a "sequence" atribute which can chosen between "ramp", "step", "map" or "control".
    The controller thread will manage what the algorithm must do for each sequence.

@@

\subsection{Step}

@@

During the cone-jet, multiple parameters and variables influence the current, flow rate and voltage operational window. The operational window, seen in Figure \ref{fig:ganan_calvo_fig} can be defined where the cone jet spraying mode can be stabilized based on the flow rate, voltage and the setup configuration\cite{gananCalvo}.

@@

@@

\section{System Portability}
\label{sec:portability}

    Raspberry Pi

>>>>

This chapter is about describing the metodology and developments to achieve the project goals. 
The python routine which this project is about was developed by the previous student that worked on it.\cite{Monica}
The software was previously developed as a electrospray multipurpose library\cite{Monica}.

The works therefore presented here are a continuation and optimization of the routine to make it more precise and applicable to both industrial and research approaches.

@@

    \subsection{Data Acquisition Thread}
    \label{subsec:data_aquisition}

@@

    The program developed is capable of running different types of routines. The code is also easy to implement new routines.
    Continuing the methodology, in the setup json file there is a "sequence" attribute which can be chosen between "ramp", "step", "map" or "control".
    The controller thread will manage what the algorithm must do for each sequence.
    Following our control model\ref{fig:control_model_fig}, the controller outputs are the actuators signal.
    The sampling rate is fixed to 0.5 seconds for all the experiments, and it's managed by the data\_acquisiton thread\ref{subsec:data_aquisition}.

@@

\subsection{Step}
\label{subsec:step_routine}

@@

The map that will be explained bellow is the most relevant sequence in this work. This type of experiment saves human work and time, create a precise analysis and can be compared with previous works for validation of methodology.
The purpose is to map the operational window, seen in Figure \ref{fig:ganan_calvo_fig}, that can be defined where the cone jet spraying mode can be stabilized based on the flow rate, voltage and the setup configuration\cite{gananCalvo}.

@@

To reach certain map it is necessary to traverse flow rate and voltage values acquiring samples.
The flow rate (X axis) and voltage (Y axis) values for each experiment can be configured in the setup.json file.
The algorithm for this sequence is a copy of the step sequence\ref{subsec:step_routine} for each flow rate chosen. It is illustrated in the algorithm \ref{alg:mapping_algorithm}.

@@
